### 2014-03-08 src/analysis.Rnw
update

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#myopts <- theme(panel.background = element_blank())
#myopts <-   theme_bw() +
#  opts(axis.line = theme_segment(colour = "black"),
#    panel.grid.major = theme_blank(),
#    panel.grid.minor = theme_blank(),
#    panel.border = theme_blank(),
#    panel.background = theme_blank()) 
  #theme with white background
myopts <- theme_bw() +
  #eliminates background, gridlines, and chart border
  theme(
    plot.background = element_blank()
   ,panel.grid.major = element_blank()
   ,panel.grid.minor = element_blank()
   ,panel.border = element_blank()
  ) + 
  #draws x and y axis line
  theme(axis.line = element_line(color = 'black'))
myopts <-  theme_classic() 
#+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))

>>>>

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
theme_set(theme_bw(24))
#myopts <- theme(panel.background = element_blank())
#myopts <-   theme_bw() +
#  opts(axis.line = theme_segment(colour = "black"),
#    panel.grid.major = theme_blank(),
#    panel.grid.minor = theme_blank(),
#    panel.border = theme_blank(),
#    panel.background = theme_blank()) 
  #theme with white background
myopts <- theme_bw() +
  #eliminates background, gridlines, and chart border
  theme(
    plot.background = element_blank()
   ,panel.grid.major = element_blank()
   ,panel.grid.minor = element_blank()
   ,panel.border = element_blank()
  ) + 
  #draws x and y axis line
  theme(axis.line = element_line(color = 'black'))
myopts <-  opts() #theme_classic() 
#+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))

### 2014-03-08 src/paper.Rnw
update

\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
% 10 pages for the main text + 1 for references.
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='conclusion.Rnw'>>=
@

>>>>

\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
% 10 pages for the main text + 1 for references.
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<conclusion, child='conclusion.Rnw'>>=
@
